A Triple Origin for Twin Blue Stragglers in Compact Binaries

### 2018-12-13 BSS7782.tex
testing

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  We assume circular orbits for both the inner and outer
orbits, and co-planar triples only since this is what has been
observed for low-mass tertiaries \cite{2010yCat..73890925T} \simon{I
  think that {\em moe18} and {\em tobin18} are not the right
  references - NL: I am fine with swapping out this figure for another, ultimately.  It still does need work.  Could you send me the files you have for radius as a function of primary mass?  I can then update the figure with that, using your assumed initial masses for the simulations.  That *would* basically finish everything I had intended with the figure, so if we still want to remove it after that, that is totally fine.}.  This initial configuration for our assumed formation
scenario for Binary 7782, described below, is depicted in
Figure~\ref{fig:fig1}.

@@

We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$
and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components,
and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
\cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
time the star has lost 0.13\,\MSun\, via a stellar wind.  With these
parameters the orbital separation of the outer binary becomes 3.86\,au,
and the mass loss has driven a slight eccentricity deviating from an initially
circular orbit to about 0.0082 at the moment of Roche-lobe
overflow. We choose a relative initial inclination of $i = 9^\circ$
between the inner and the outer orbits.
%NL: What are the initial orbital separations?

In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
system at the onset of Roche-lobe overlofw.

@@

\item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.  This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{haiman09,farris15,rafikov16,kelley17}.  This quickly brings the mass ratio toward unity.  This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.  This could be observable in the surface layers of a radiative star.  If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.  If the donor is an AGB star, it will be enriched in mostly s-process elements.

>>>>

Consider a hierarchical triple system with component masses m$_{\rm
  1}$ and m$_{\rm 2}$ for the inner binary, and mass m$_{\rm 3}$ for
the outer tertiary companion.  The inner and outer binary orbital
semi-major axes are denoted a$_{\rm in}$ and a$_{\rm out}$,
respectively.  We assume circular orbits for both the inner and outer
orbits, and co-planar triples only since this is what has been
observed for low-mass tertiaries \cite{2010yCat..73890925T,moe18} \simon{I
  think that {\em moe18} and {\em tobin18} are not the right
  references - NL: I checked and I think the moe18 reference, at least, is fine, so I added it back in.  But feel free to remove it, if you prefer.}.  This initial configuration for our assumed formation
scenario for Binary 7782, described below, is depicted in
Figure~\ref{fig:fig1}.

@@

We adopt initial component masses of m$_{\rm 1}$ = 1.1 M$_{\rm \odot}$
and m$_{\rm 2}$ = 0.9 M$_{\rm \odot}$ for the inner binary components,
and m$_{\rm 3}$ = 1.2 M$_{\rm \odot}$ for the tertiary star.  We
evolve the 1.2\,\MSun\, star using the MESA stellar evolution code
\cite{2011ApJS..192....3P} to a radius of about 255\,\RSun.  By this
time the star has lost 0.13\,\MSun\, via a stellar wind.  With these
parameters the orbital separation of the outer binary becomes 3.86\,au,
and the mass loss has driven a slight eccentricity deviating from an initially
circular orbit to about 0.0082 at the moment of Roche-lobe
overflow. We choose a relative initial inclination of $i = 9^\circ$
between the inner and the outer orbits, since observed stellar triples composed of low-mass stars have been observed to favor co-planar configurations \citep{moe18}.
%NL: What are the initial orbital separations?  Why this choice of initial inclination? - I added a sentence and reference to justify it.

In fig.\,\ref{fig:topview_at_t0} we present a top view of the triple
system at the onset of Roche-lobe overflow.

@@

\item The BSs in the inner binary should have roughly equal masses, independent of their initial masses.  This is because it is the lowest mass object that typically accretes the fastest, since its orbital velocity and distance relative to the circumbinary disk is typically the lowest \citep[e.g.][]{kroupa95,bate97,bate00,haiman09,bate12,farris15,rafikov16,kelley17}.  This quickly brings the mass ratio toward unity.  This predicts that the initially lower mass MS star should accrete the most, and should hence be polluted more significantly by any accreted material.  This could be observable in the surface layers of a radiative star.  If the donor is an RGB star, the accretor will be enriched in mostly carbon, oxygen and helium.  If the donor is an AGB star, it will be enriched in mostly s-process elements.
